Arc Blanc: a real time ocean simulation framework

### 2025-01-31 paper.tex
Add pseudo code on water height calculation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Water displacement and derivative}

\Framework uses the horizontal displacement $\mathbf{D}(\mathbf x,t) = \left[D_x(\mathbf x,t)\ D_z(\mathbf x,t)\right]^T$ of seawater to simulate more realistic choppy waves.
As proposed in Sections 4.5 and 4.6 of Tessendorf (2001) \cite{tessendorfSimulating2001}, it is calculated as follows:
\begin{equation}\label{equa:hori-displacement}
	\mathbf{D}(\mathbf x,t) = \sum_{\mathbf{k}} \mathbf{\tilde{D}}(\mathbf k,t)\exp\left(i\mathbf{k}\cdot\mathbf x\right)
\end{equation}

@@

@@

\end{proof}
%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%
\afterdoc
%%%%%%%%%%%%%%%
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Water displacement and derivative}
\label{subsec:water_displacement_and_derivative}
\Framework uses the horizontal displacement $\mathbf{D}(\mathbf x,t) = \left[D_x(\mathbf x,t)\ D_z(\mathbf x,t)\right]^T$ of seawater to simulate more realistic choppy waves.
As proposed in Sections 4.5 and 4.6 of Tessendorf (2001) \cite{tessendorfSimulating2001}, it is calculated as follows:
\begin{equation}\label{equa:hori-displacement}
	\mathbf{D}(\mathbf x,t) = \sum_{\mathbf{k}} \mathbf{\tilde{D}}(\mathbf k,t)\exp\left(i\mathbf{k}\cdot\mathbf x\right)
\end{equation}

@@

To compute the water height at a specific point, it is not sufficient to directly evaluate Equation \ref{equa:heightWater} after performing the IFFT. This is because the water surface is described parametrically, with fluid positions depending on both horizontal and vertical displacements, as detailed in Section \ref{subsec:water_displacement_and_derivative}. Accurately determining the water surface position at a given horizontal location requires an iterative process (see Algorithm \ref{alg:compute_water_height}): the estimated position is adjusted by subtracting the displacement vector, and the water height is recalculated until convergence. However, in practice, waiting for full convergence may be computationally expensive. Instead, the loop is limited to $N_{iter}=4$ iterations, a value chosen to balance accuracy and performance (see Appendix \ref{sec:evaluation_of_the_number_of_iterations_for_convergence} for details on this choice).

\input{Algorithms/water_height.tex}

@@

\end{proof}

\section{Evaluation of the Number of Iterations for Convergence}
\label{sec:evaluation_of_the_number_of_iterations_for_convergence}
The optimal number of iterations ($N_{\text{iter}}$) required for the iterative retrieval of the water height was determined through a series of tests. Wind speeds were varied from $0.1 \, \text{m/s}$ to $35.0 \, \text{m/s}$ in increments of $0.5 \, \text{m/s}$, and the convergence of water height was evaluated at $1000$ random positions over a $10^4 \, \text{m} \times 10^4 \, \text{m}$ domain.

The program iteratively computed the water height until the changes in height were smaller than a $1$ cm.

The results, as shown in Figure~\ref{fig:convergence_steps}, demonstrate that the required number of iterations increases with wind speed, stabilizing at approximately $N_{\text{iter}} = 4$ for higher wind speeds. This finding suggests that using $N_{\text{iter}} = 4$ ensures reliable convergence for all tested conditions while balancing computational efficiency.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{Figures/results_cm.png}
    \caption{Mean number of steps required for convergence as a function of wind speed. Error bars represent the variance of iterations across $1000$ test points.}
    \label{fig:convergence_steps}
\end{figure}
%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%
\afterdoc
%%%%%%%%%%%%%%%
\end{document}
